|

### 2019-08-16 article/article.Rmd
small edits

We find that the intervention was sufficient to improve the school completion rate. The TDP application increases in `r round(100*resInt1[[2]][[16]]$coefficients[1], 1)` percent the chance that a school construction is reported as finished by the end of the intervention. This is in line with our theoretical expectations, but as we discuss below, the finding is not consistent. All other coefficients are not statistically significant at conventional levels. On the one hand, the results indicate that our placebo outcome, the percentage of the invested executed before the intervention, indeed behaves as predicted. On the other hand, we expected the four remaining outcomes to increase after the introduction of the app. The literature on bottom-up accountability argues that more information about the shortcomings of public service provision will mobilise citizens who, in turn, would pressure state agents to produce better social policies. Our results do not lend support to that hypothesis.

@@

What factors, then, are driving these results? It seems unlikely that the null results derive from flaws in the research design. First, our study is well powered. About 1,000 municipalities were included in the treatment groups, thus we should be able to capture average treatment effects, even small ones, if they indeed exist. Second, balance and manipulation tests indicate that the treatment allocation was successful, so we can rule out problems in the randomisation procedures. Third, after doing a series of robustness tests --- including matching and randomised inference --- we still find no evidence of treatment effect.

@@

Moreover, it is possible that a mobile app like TDP is simply not sufficient to promote collective action. @raffler2018weakness [29] point out several reasons why information interventions does not lead to higher pressure on public agents, such as citizens' apathy towards their ability to make public agents accountable, lack of official channels to support popular demands, or that constituents have more pressing needs than monitoring representatives. Furthermore, individuals may also believe they are better-off by free-riding on other users of the TDP app, thus reaping the benefits of having faster school constructions without incurring personal costs [@olson1965logic].

>>>>

We find that the intervention is sufficient to improve school completion rates. The TDP application increases in `r round(100*resInt1[[2]][[16]]$coefficients[1], 1)` percent the chance that a school construction is reported as finished by the end of the intervention. This is in line with our theoretical expectations, but as we discuss below, the finding is not consistent. All other coefficients are not statistically significant at conventional levels. On the one hand, the results indicate that our placebo outcome, the percentage of the invested executed before the intervention, indeed behaves as predicted. On the other hand, we expected the four remaining outcomes to increase after the introduction of the app. The literature on bottom-up accountability argues that more information about the shortcomings of public service provision will mobilise citizens who, in turn, would pressure state agents to produce better social policies. Our results do not lend support to that hypothesis.

@@

What factors, then, are driving these results? It seems unlikely that the null results derive from flaws in the research design. First, our study is well powered. We included 1000 municipalities in the treatment groups, thus we should be able to capture small average treatment effects if they exist. Second, balance and manipulation tests indicate that the treatment allocation was successful, so we can rule out problems in the randomisation procedures. Third, after doing a series of robustness tests --- including matching and randomised inference --- we still find no firm evidence of treatment effect.

@@

Moreover, it is possible that a mobile app like TDP is simply not sufficient to promote collective action. @raffler2018weakness [29] point out several reasons why information interventions does not lead to higher pressure on public agents, such as citizens' apathy towards their ability to make public agents accountable, lack of official channels to support popular demands, or that constituents have more pressing needs than monitoring representatives. Furthermore, individuals may also believe they are better off by free-riding on other users of the TDP app, thus reaping the benefits of having faster school constructions without incurring personal costs [@olson1965logic].
